\pkg{fitdistrplus}: An \proglang{R} Package for Fitting Distributions

### 2014-02-11 JSS/fitdistrplus/paper2JSS.Rnw
new definition of authors, maintainer and contributors in the Description file and minor changes in paper2JSS
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/riskassessment@273 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

A classical data set from the Danish insurance industry 
published in \cite{mcneil97} will be used to illustrate this method.
In \pkg{fitdistrplus}, the data set is stored in \code{danishuni} for the univariate version and contains
the loss amounts collected at Copenhagen Reinsurance between 1980 and 1990.
In actuarial science, it is standard to consider positive heavy-tailed distributions and have 
a special focus on the right-tail of the distributions.
In this numerical experiment, we choose classic actuarial 
distributions for loss modelling: the lognormal distribution and the Pareto type II 
distribution, see e.g. \citep{Klugmanetal09}.

>>>>

A classical data set from the Danish insurance industry 
published in \cite{mcneil97} will be used to illustrate this method.
In \pkg{fitdistrplus}, the data set is stored in \code{danishuni} for the univariate version and contains
the loss amounts collected at Copenhagen Reinsurance between 1980 and 1990.
In actuarial science, it is standard to consider positive heavy-tailed distributions and have 
a special focus on the right-tail of the distributions.
In this numerical experiment, we choose classic actuarial 
distributions for loss modelling: the lognormal distribution and the Pareto type II 
distribution \citep{Klugmanetal09}.
